Exploratory_Analysis_Josh_Tobey

### 2025-11-18 Exploratory_Analysis_Josh_Tobey.Rmd
Second attempt at test push
Second Attempt

---
title: "Exploratory_Analysis_Josh_Tobey"
author: "Joshua Tobey"
date: "2025-11-17"
output: html_document
---
```{r}

```

>>>>

---
title: "Exploratory_Analysis_Josh_Tobey"
author: "Joshua Tobey"
date: "2025-11-17"
output: html_document
---
```{r}
print("Push test for exploratory analysis")
install.packages(c("usethis", "gitcreds"))
```
